Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2023-09-12 Paper/Supplementary.tex
Improve description for symbol u

$\gain(\along,\athw,\samplesymf)$ & & 1 & Transducer gain as a function of echo arrival angle in the beam and frequency index.\\

@@

$\channelsym$ & & 1 & Channel number/transducer sector.\\
$u(\genidxsym)$ & & 1 & The Heaviside step function. \\
$V$ & & $\textrm{m}^3$ & Volume occupied by scattering targets.\\
$\stagesym$ & & 1 & Filter stage.\\

@@

$\yrx(\samplesymt,\channelsym)$ & & V & Received digitised, bandpass filtered, decimated complex signal after the final filter stage, $\yrx(\samplesymt,\channelsym) = \yrx(\samplesymt,\channelsym,\nstages)$.\\
$\yrx(\samplesymt,\channelsym,\stagesym)$ & & V & Received digitised, bandpass filtered, decimated complex signal.\\
$\yrxa(\timesym)$ & & Pa & Analogue acoustic signal received by the transducer.\\
$\yrxa(\timesym,\channelsym)$ & & Pa & Analogue acoustic signal received by each transducer sector $\channelsym$.\\
$\yrxe(\timesym,\channelsym)$ & & V & Analogue electric signal received by each transceiver channel $\channelsym$.\\

@@

$\absorp(\freqsym)$  & & dB $\textrm{m}^{-1}$ & Absorption coefficient at frequency $f$.\\
$\absorp(\samplesymf)$ & & dB $\textrm{m}^{-1}$ & Absorption coefficient at frequency index $m$\\
$\anglefalong$ & & 1 & Conversion factor between phase difference in signals from the fore and aft transducer halves and the physical arrival angle of an echo.\\
$\anglefathw$ & & 1 & Conversion factor between phase difference in signals from the port and starboard transducer halves and the physical arrival angle of an echo.\\
$\along$ & & rad & Angle coordinates along the minor axis of the transducer (alongship when ship-mounted).\\
$\along(\samplesymt)$ & & rad & Angle of arrival of target echo along the minor axis of the transducer (alongship when ship-mounted).\\
$\wlen$ & & m &  Acoustic wavelength.\\
$\wlen_\samplesymf$ & & m & Acoustic wavelength at frequency index $m$\\
$\sigmabs$ & & $\textrm{m}^2$ & Backscattering cross-section.\\
$\tnom$ & & s & Nominal transmit pulse duration.\\
$\teff$ & & s & Effective transmit pulse duration.\\
$\athw$ & & rad & Angle coordinates along the major axis of the transducer (athwartship when ship-mounted).\\
$\athw(\samplesymt)$ & & rad & Angle of arrival of target echo along the major axis of the transducer (athwartship when ship-mounted).\\
$\eqang(\freqsym)$ & & sr & Two-way equivalent beam angle at frequency $\freqsym$.\\
\end{longtable}

>>>>

% $\gain(\along,\athw,\samplesymf)$ & & 1 & Transducer gain as a function of echo arrival angle in the beam and frequency index.\\

@@

$\channelsym$ & & 1 & Receiver channel number and transducer sector number.\\
$u(\genidxsym)$ & & 1 & The Heaviside step function. \\
$V$ & & $\textrm{m}^3$ & Volume occupied by scattering targets.\\
$\stagesym$ & & 1 & Filter stage.\\

@@

$\yrx(\samplesymt,\channelsym)$ & & V & Received digitised, bandpass filtered, decimated complex signal after the final filter stage, $\yrx(\samplesymt,\channelsym) = \yrx(\samplesymt,\channelsym,\nstages)$.\\
$\yrx(\samplesymt,\channelsym,\stagesym)$ & & V & Received digitised, bandpass filtered, decimated complex signal.\\
$\yrxa(\timesym)$ & & Pa & Analogue acoustic signal received by the transducer.\\
% $\yrxa(\timesym,\channelsym)$ & & Pa & Analogue acoustic signal received by each transducer sector $\channelsym$.\\
$\yrxe(\timesym,\channelsym)$ & & V & Analogue electric signal received by each transceiver channel $\channelsym$.\\

@@

$\absorp(\freqsym)$  & & dB $\textrm{m}^{-1}$ & Absorption coefficient at frequency $f$.\\
% $\absorp(\samplesymf)$ & & dB $\textrm{m}^{-1}$ & Absorption coefficient at frequency index $m$\\
$\anglefalong$ & & 1 & Conversion factor between phase difference in signals from the fore and aft transducer halves and the physical arrival angle of an echo.\\
$\anglefathw$ & & 1 & Conversion factor between phase difference in signals from the port and starboard transducer halves and the physical arrival angle of an echo.\\
$\along$ & & rad & Angle coordinates along the minor axis of the transducer (alongship when ship-mounted).\\
% $\along(\samplesymt)$ & & rad & Angle of arrival of target echo along the minor axis of the transducer (alongship when ship-mounted).\\
$\wlen$ & & m &  Acoustic wavelength.\\
$\wlen_\samplesymf$ & & m & Acoustic wavelength at frequency index $m$\\
$\sigmabs$ & & $\textrm{m}^2$ & Backscattering cross-section.\\
$\tnom$ & & s & Nominal transmit pulse duration.\\
$\teff$ & & s & Effective transmit pulse duration.\\
$\athw$ & & rad & Angle coordinates along the major axis of the transducer (athwartship when ship-mounted).\\
% $\athw(\samplesymt)$ & & rad & Angle of arrival of target echo along the major axis of the transducer (athwartship when ship-mounted).\\
$\eqang(\freqsym)$ & & sr & Two-way equivalent beam angle at frequency $\freqsym$.\\
\end{longtable}
